
\begin{itemize}
    \item Ajayakumar, J., Curtis, A. J., Maisha, F. M., Bempah, S., Ali, A., \textbf{Kannan, N.}, Armstrong, G. \& Morris Jr, J. G. (2024). Using spatial video and deep learning for automated mapping of ground-level context in relief camps. International Journal of Health Geographics, 23(1), 23. 
    \item Ruksakulpiwat, S., Thongking, W., \textbf{Kannan, N.}, Wright, E., Niyomyart, A., Benjasirisan, C., ... \& Still, C. H. (2024). Understanding the Relationship Between Comorbidities, Medication Nonadherence, Activities of Daily Living, and Heart Condition Status Among Older Adults in the United States: A Regression Analysis and Machine Learning Approach. Journal of Cardiovascular Nursing, 10-1097.
    \item \textbf{Naveen Kannan}\textsuperscript{1}, Nicholas Wheeler\textsuperscript{1}, Genome Center for Alzheimer’s Disease, Li-San Wang\textsuperscript{2}, Yuk Yee Leung\textsuperscript{2}, William S. Bush\textsuperscript{1},\textsuperscript{1}Cleveland Institute for Computational Biology, Department for Population and Quantitative Health Sciences, Case Western Reserve University, Cleveland, Ohio 44106, USA;\textsuperscript{2} Department of Pathology and Laboratory Medicine, Penn Neurodegeneration Genomics Center, Perelman School of Medicine, University of Pennsylvania, Philadelphia, Pennsylvania 19104, USA, Quality Control metrics of individual genetic variants in the Alzheimer’s Disease Sequencing Project are associated with FAVOR annotations.
    \item Segamalai, D., Abdul Jameel, A.~R., \textbf{Kannan, N.}, Anbalagan, A., Duraisamy, B., Raju, P., \& Devy Gounder, K. (2017). \textit{Mediastinal pseudocyst: varied presentations and management---experience from a tertiary referral care centre in India}. \textit{HPB Surgery}, \textit{2017}.\\\url{https://downloads.hindawi.com/archive/2017/5247626.pdf}
    \item Vellaisamy, R., \textbf{Kannan, N.}, Anbalagan, A., Raju, P., Duraisamy, B., Murugesan, C. S., \& Gounder, K. D. (2016). Endoscopic access to hepatic duct through duodenum during follow up--after primary surgery for hepatolithiasis.\textit{HPB, 18,} e530.\\\url{https://hpbonline.org/article/S1365-182X(16)31428-9/fulltext}
    \item Ramasamy, V., Vellaisamy, R., \textbf{Kannan, N.}, \& Gounder, K. D. (2016). Refined technique of access loop in hepatobiliary surgery.\textit{HPB, 18}, e593-e594. \\\url{https://hpbonline.org/article/S1365-182X(16)31598-2/abstract}
    \item \textbf{Kannan, N.}, Vellaisamy, R., Govindarajan, M., \& Gounder, K. D. (2016). Pellagra following pancreaticoduodenectomy for malignant pancreatic carcinoid with pluripotent hormonal potential. \textit{HPB, 18}, e381-e382 \\\url{https://www.hpbonline.org/article/S1365-182X(16)31013-9/fulltext}
    
\end{itemize}



