% Your second paragraph should be a brief overview of your background as is relevant to the position. Here, you should include key achievements, skills and specialties that make you particularly suited to perform well in the position. Focus on one or two and provide specific details about your success including measurable impacts you made.

% Pay close attention to keywords listed in the job description and include those that you identify with in the body of your cover letter. You should only include information about your most recent one or two professional experiences.

% https://www.indeed.com/career-advice/resumes-cover-letters/how-to-write-a-cover-letter

As the sole Data Engineer at Trailhead Biosystems, I am a key technical leader responsible for integrating complex, discrete, non-standard data sources into a normalized relational database, enabling streamlined analysis and reporting. I develop and maintain RESTful APIs and Django-based web applications to support internal stakeholders, including scientific and operations personnel. I implement secure, cloud-based infrastructure (Azure VMs along with Microsoft Entra) with an emphasis on data integrity, access control, and compliance with internal standards. I am building a fully version-controlled informatics tech stack to support reproducible research from the ground up. This work has unlocked high-resolution, data-driven insights and facilitated dashboarding and visualization for decision-making at a scale and depth that did not exist before.

Prior to that, I was a Research Associate at Case Western Reserve University, where I managed large-scale genomic data in collaboration with the Alzheimer’s Disease Sequencing Project. I automated the deployment of a HDFS cluster using custom Ansible scripts on a bare-metal 18 node computing cluster, along with distributed bioinformatics frameworks like Spark, Hail, and Glow, enabling the storage and annotation of 362 million Alzheimer’s-linked structural genetic variants and supporting multiple peer-reviewed publications that I contributed to. I connected our bare-metal servers to cloud infrastructure (AWS EC2, S3, RDS), enabling hybrid workflows that supported scalable, automated and reproducible pipeline execution via Docker containers deployed in a HPC environment. 
